Temporal Split

### 2023-01-25 workflow/notebooks/temporal-split.Rmd
Echo code chunks

```{r setup, include=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      fig.path = 'figures/')
```

@@

int_pctl(boots, perf)
```

@@

```{r temporal-split_perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>% #, 'prAUC')) %>% 
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  facet_wrap('dataset') +
  theme_sovacool()
```

>>>>

```{r setup, include=FALSE}
schtools::set_knitr_opts()
knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE,
                      echo = TRUE,
                      fig.path = 'figures/')
```

@@

int_pctl(boots, perf) %>% kable()
```

@@

```{r temporal-split_perf-95-ci}
perf_dat <- read_csv(here('results','temporal-split','performance_results.csv'))
perf_dat %>% 
  filter(term %in% c('cv_metric_AUC', "AUC")) %>%
  mutate(term = case_when(term == 'cv_metric_AUC' ~ 'train AUROC',
                          term == 'AUC' ~ 'test AUROC',
                          TRUE ~ term)
  ) %>% 
  rename(estimate = .estimate,
         lower = .lower,
         upper = .upper) %>% 
  ggplot(aes(x = estimate, xmin = lower, xmax = upper, y = outcome, color = term)) +
  geom_pointrange(position = position_dodge(width = 0.1)) +
  facet_wrap('dataset') +
  theme_sovacool()
```
